Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-01-21 curriculo/cv.tex
[ADD] local video\n[FIX] mic off on leave

%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{Henrique}{Rocha}
       {Telecommunications and Informatics}

% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    Henrique Duarte Lopes Rocha
    ~
    Rua dos Cedros nº100
    Alto do Lagoal
    2760-025 Caxias
    Portugal
    ~
    (+351) 938781922
    ~
    \href{mailto:hdlopesrocha91@gmail.com}{hdlopesrocha91\\@gmail.com}
    \href{http://web.ist.utl.pt/ist168621}{WebSite}
    \href{http://www.youtube.com/user/hdlopesrocha}{YouTube}
  \section{languages}
    portuguese (native)
    english (fluent)
  \section{programming}
    {\color{red} $\varheartsuit$} Java
	 (Android, PlayFramework, LWJGL, MapReduce, GWT, AWS), C, C++ (OpenGL), C\# (XNA, Windows Forms, WPF, lpsolve), VB, Python, Scala, Scheme, HTML, CSS (Bootstrap), JavaScript (jQuery, AJAX, WebGL, WebRTC), PHP (Wordpress), GLSL, HLSL.  
   \section{databases}
	DynamoDB, MongoDB, MySQL, Neo4j, PostgreSQL, SQLite.
   \section{soft skills}
	Time Management
	Problem-Solving
	Team Player
	Self Confidence
	Adaptability
\end{aside}

@@

\begin{entrylist}
   \entry
    {2013–now}
    {Master of Science}
    {Instituto Superior Técnico - Taguspark}
    {Telecommunications and Informatics Engineering}

   \entry
    {2009–2014}
    {Bachelor of Science}
    {Instituto Superior Técnico - Taguspark}
    {Communication Networks Engineering}

@@

%\section{publications}

%Put your publications here!

%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
% 
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

>>>>

%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}
\begin{document}
\header{Henrique}{Rocha}
       {Telecommunications and Informatics}

% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    Henrique Duarte Lopes Rocha
    ~
    Rua dos Cedros nº100
    Alto do Lagoal
    2760-025 Caxias
    Portugal
    ~
    (+351) 938781922
    ~
    \href{mailto:hdlopesrocha91@gmail.com}{hdlopesrocha91@gmail.com}
    \href{http://web.ist.utl.pt/ist168621}{WebSite}
    \href{http://www.youtube.com/user/hdlopesrocha}{YouTube}
  \section{languages}
    portuguese (native)
    english (fluent)
  \section{programming}
    {\color{red} $\varheartsuit$} Java
	 (Android, PlayFramework, LWJGL, MapReduce, GWT, AWS), C, C++ (OpenGL), C\# (XNA, Windows Forms, WPF, lpsolve), VB, Python, Scala, Scheme, HTML, CSS (Bootstrap), JavaScript (jQuery, AJAX, WebGL, WebRTC), PHP (Wordpress), GLSL, HLSL.  
   \section{databases}
	DynamoDB, MongoDB, MySQL, Neo4j, PostgreSQL, SQLite.
   \section{soft skills}
	Time Management
	Problem-Solving
	Team Player
	Self Confidence
	Adaptability
\end{aside}

@@

\begin{entrylist}
   \entry
    {2013–now}
    {Master of Science}
    {Instituto Superior Técnico - Taguspark}
    {Telecommunications and Informatics Engineering (Expected Grade: 16 in 20)}
   \entry
    {2009–2014}
    {Bachelor of Science}
    {Instituto Superior Técnico - Taguspark}
    {Communication Networks Engineering (Final Grade: 13.2 in 20)}

@@

\newpage
\section{grades}
\subsection{Bachelor - Communication Networks Engineering}
\input{grades_bachelor.tex}
\subsection{Master - Telecommunications and Informatics Engineering}
\input{grades_master.tex}
